---
title: "Home Prices EDA and Machine Learning"
output: html_document
---

```{r setup, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```


#### Add Libraries
```{r}
library(data.table)
library(ggplot2)
library(ggthemes)
library(glmnet)
library(plotly)
theme_set(theme_bw())
```

#### Load in dataset
```{r}
trainPrice <- fread("trainPrice.csv")
```

#### First few rows
```{r}
head(trainPrice, 5)
```

#### Structure of the dataset
```{r}
str(trainPrice)
```


#### Randomize the rows
```{r}
set.seed(42)
rows <- sample(nrow(trainPrice))
trainPrice <- trainPrice[rows, ]
```


#### Linear model of price and city (the first 50000 observations)
```{r}
ggplot(head(trainPrice, 50000), aes(x = city
, y=transaction_real_price)) +
  geom_point(alpha = 0.4)+
  stat_smooth(
    method = "lm",
    color = "#C42126",
    se = FALSE,
    size = 1
  )
```

#### Set city and room count as factor
```{r}
trainPrice <- trainPrice[, city:=as.factor(city)]
trainPrice <- trainPrice[, room_count:=as.factor(room_count)]
```

#### remove null values
```{r}
trainPrice <- trainPrice[!is.na(room_count)]
```



#### Barchart showing real price and city
```{r}
ggplot(trainPrice, aes(x=city, y = transaction_real_price)) + 
  geom_bar(stat = "summary", fun = "mean")+
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  theme_classic()
```

#### Barchart showing real price and room count
```{r}
ggplot(trainPrice, aes(x=room_count, y = transaction_real_price)) + 
  geom_bar(stat = "summary", fun = "mean")+
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  theme_classic()
```

#### Linear regression model of exclusive use area vs real price
```{r}
ggplot(trainPrice, aes(x = exclusive_use_area, y=transaction_real_price)) +
  geom_point(alpha = 0.4)
```



####Plotly Map

##### 1 is seoul
##### 0 is Busan

##### Styling
<!-- g <- list( -->
<!--   fitbounds = "locations", -->
<!--   height=300, -->
<!--   zoom=10, -->
<!--   scope = 'asia', -->
<!--   lataxis_range=(-50,20), -->
<!--   lonaxis_range=(0, 200) -->
<!--  # visible = FALSE, -->
<!--  # showland = TRUE, -->
<!--  # landcolor = toRGB("gray95"), -->
<!--  # subunitcolor = toRGB("gray85"), -->
<!--  # countrycolor = toRGB("gray85"), -->
<!--  # countrywidth = 0.5, -->
<!--   #subunitwidth = 0.5 -->
<!-- ) -->

##### Figure
<!-- fig <- plot_geo(small_set, lat = ~latitude, lon = ~longitude) -->

<!-- fig <- fig %>% add_markers( -->
<!--   text = ~paste(latitude, longitude, room_count, paste("Price:", transaction_real_price), sep = "<br />"), -->
<!--   color = ~transaction_real_price, symbol = I("square"), size = I(8), hoverinfo = "text" -->
<!-- ) -->
<!-- fig <- fig %>% colorbar(title = "Incoming flights<br />February 2011") -->
<!-- fig <- fig %>% layout( -->
<!--   title = 'Most trafficked US airports<br />(Hover for airport)', geo = g -->
<!-- ) -->

<!-- fig -->


